\huge ARuko and Editour: \\ \Large A Platform for Augmented Reality Tour Guide Apps

### 2019-09-27 paper.tex
add a lot of stuff
Add Appendix B, fix grammar, add citations, add images, add final field
testing section, add list of tables, clean up table of contents, and
rearrange some sections.

\usepackage{lipsum} % lorem-ipsum placeholder text
\usepackage{bookmark} % links to other parts of the PDF
% if we want to use a different style, here are some to look at
% https://www.overleaf.com/learn/latex/Biblatex_bibliography_styles
\usepackage[backend=biber,style=numeric,sorting=none]{biblatex} % citations
\usepackage[page, titletoc, title]{appendix} % labeled appendices
\usepackage[margin=1in]{geometry} % set 1in margins
\usepackage{hyperref} % hyperlinks
\usepackage{setspace} % setting custom spacing

@@

% now comes the table of contents, list of figures, and list of tables
% these should be single spaced
\begin{singlespace}
	\tableofcontents
	% add table of contents to itself
	\addcontentsline{toc}{section}{Table of Contents}
	\newpage

	\listoffigures
	\addcontentsline{toc}{section}{List of Figures}
	\newpage
\end{singlespace}

% we don't have any tables yet, but uncomment this when we do
%\addcontentsline{toc}{section}{List of Tables}
%\listoftables
%\newpage

@@

While preparing for this project our team researched the current state of
augmented reality technology. Smartphones are the most commonly used AR
hardware by far [citation needed]. Typically smartphone AR applications make
use of the phone's camera, accelerometer, gyroscope, and GPS sensors to
reproduce a view of the real world with virtual information layered on top of
it~\autocite{bonsor2018}.

@@

According to Techopedia, ``Emulation is the process of imitating a
hardware/software program/platform on another program or platform. This makes
it possible to run programs on systems not designed for
them''~\autocite{techopedia2019}. Emulators are often very useful for speeding
up development. Loading programs onto the Android emulator usually much faster
than installing the APK onto the actual device. Additionally, you can mock
almost all of the important features of an actual Android device, including
calls, text, GPS position, device rotation and more \autocite{androidemulator}.

Since an emulator uses software to emulate hardware, this poses two technical
issues that prevent emulators from being a proper replacement for testing on
real hardware.  Emulation is often imperfect, so glitches sometimes emerge in
emulation that do not manifest on the actual hardware [citation needed about
emulator inaccuracies]. Conversely, errors that exist in the hardware version
may not appear in the emulation. Secondly, and most importantly for AR, it is
common for emulation to be much slower compared to real hardware.

@@

One of the goals for our project is to create a working prototype that others
can build off of in the future [citation needed for personal communication].

Similar to the app izi.TRAVEL discussed in section~\ref{sec:iziTravel}, we
needed some way to easily define arbitrary polygons (which we call ``regions'')
and associate media with each one, such as audio and image files.

For testing purposes, we initially defined these regions directly in the C\#
Scripts, hard-coding the coordinates. [citation needed for source used to
write polygon detection code] Below is an example of a quadrilateral
surrounding the Creation Core building at the Ritsumeikan Biwako-Kusatsu
campus.

@@

Even with knowledge of C\# and Unity, inputting tour data this way is obviously
not convenient. Atticus reminded us that, although he has a working knowledge
of Unity, he is not a software developer [citation needed for personal
communication.] In order to make our app prototype at all useful for the
future, we needed to provide an easy way to ``design'' a tour.

@@

@@

\begin{figure}[h] \centering
    \includegraphics[width=0.5\textwidth]{sign-translation.png}
    \caption{Translated sign using AR camera}
    \label{fig:signTranslation}
\end{figure}

@@

\subsubsection{Unit Testing ARuko}
\label{sec:unitTestingARuko}

One decent algorithm for accomplishing this is by drawing a ray from a given
point to infinity. Barring edge cases (which will be discussed shortly) the
point is inside the polygon if the ray passes through an even number of line
segments.  The point is outside of the polygon if the ray intersects an odd
number of times. Figure~\ref{fig:intersectionsDiagram} should make it clear why
this works. This algorithm runs in $O(n)$, where $n$ is the sum total of the
number of vertices of all of the polygons being tested
~\autocite{geeksforgeekspolygon}.

\subsection{Editour Frontend Testing}
\label{sec:editourFrontendTesting}

@@

@@

On September 26\textsuperscript{th} we returned to Kinkaku-ji with a nearly
complete version of the ARuko in order to conduct some final testing.

@@

\section{3D Spatialized Audio Tour}
\label{sec:3dSpatializedAudioTour}

@@

\section{}

Appendix two text goes here.

>>>>

\usepackage{lipsum} % lorem-ipsum placeholder text
\usepackage{bookmark} % links to other parts of the PDF
% if we want to use a different style, here are some to look at
% https://www.overleaf.com/learn/latex/Biblatex_bibliography_styles
\usepackage[backend=biber,style=numeric,sorting=none]{biblatex} % citations
\usepackage[page, titletoc, title]{appendix} % labeled appendices
\usepackage[margin=1in]{geometry} % set 1in margins
\usepackage{hyperref} % hyperlinks
\usepackage{setspace} % setting custom spacing
\usepackage{tabulary} % nicer tables

@@

% now comes the table of contents, list of figures, and list of tables
% these should be single spaced
\begin{singlespace}
	\tableofcontents
	% uncomment this if you want the Table of Contents to have an entry in the
	% table of contents
	% \addcontentsline{toc}{section}{Table of Contents}
	\newpage

	\listoffigures
	% \addcontentsline{toc}{section}{List of Figures}
	\newpage

	\listoftables
	% \addcontentsline{toc}{section}{List of Tables}
	\newpage
\end{singlespace}

@@

While preparing for this project our team researched the current state of
augmented reality technology. Smartphones are the most commonly used AR hardware
by far~\autocite{boland2018}. Typically smartphone AR applications make use of
the phone's camera, accelerometer, gyroscope, and GPS sensors to reproduce a
view of the real world with virtual information layered on top of
it~\autocite{bonsor2018}.

@@

According to Techopedia, ``Emulation is the process of imitating a
hardware/software program/platform on another program or platform. This makes
it possible to run programs on systems not designed for
them''~\autocite{techopedia2019}. Emulators are often very useful for speeding
up development. Loading programs onto the Android emulator usually much faster
than installing the APK onto the actual device. Additionally, you can mock
almost all of the important features of an actual Android device, including
calls, text, GPS position, device rotation and more~\autocite{androidemulator}.

Since an emulator uses software to emulate hardware, this poses two technical
issues that prevent emulators from being a proper replacement for testing on
real hardware. Emulation is often imperfect, so glitches sometimes emerge in
emulation that do not manifest on the actual hardware~\autocite{alzaylaee2017}.
Conversely, errors that exist in the hardware version may not appear in the
emulation. Secondly, and most importantly for AR, it is common for emulation to
be much slower compared to real hardware.

@@

One of the goals for our project is to create a working prototype that others
can build off of in the future.

Similar to the app izi.TRAVEL discussed in Section~\ref{sec:iziTravel}, we
needed some way to easily define arbitrary polygons (which we call ``regions'')
and associate media with each one, such as audio and image files.

For testing purposes, we initially defined these regions directly in the C\#
Scripts, hard-coding the coordinates. Below is an example of a quadrilateral
surrounding the Creation Core building at the Ritsumeikan Biwako-Kusatsu campus.

@@

Even with knowledge of C\# and Unity, inputting tour data this way is obviously
not convenient. Atticus reminded us that, although he has a working knowledge of
Unity, he is not a software developer. In order to make our app prototype at all
useful for the future, we needed to provide an easy way to ``design'' a tour.

@@

Tours are stored on the server as compressed \texttt{.zip} files, but when
uploading or editing a tour these zips are decompressed to a temporary
directory. To prevent the server's limited disk space from filling up with old
temporary files we wrote a simple bash script that removes directories that
haven't been modified in the past five days. We set up a \texttt{cron} job to
run this script automatically once per day to clean out old temporary files that
aren't being used any more.

@@

\begin{figure}[h] \centering
    \includegraphics[width=0.3\textwidth]{sign-translation.png}
    \caption{Translated sign using AR camera}
    \label{fig:signTranslation}
\end{figure}

@@

\subsubsection{Editour Frontend Testing}
\label{sec:editourFrontendTesting}

@@

\subsection{Unit Testing ARuko}
\label{sec:unitTestingARuko}

One decent algorithm for accomplishing this is by drawing a ray from a given
point to infinity. Barring edge cases (which will be discussed shortly) the
point is inside the polygon if the ray passes through an even number of line
segments.  The point is outside of the polygon if the ray intersects an odd
number of times. Figure~\ref{fig:intersectionsDiagram} should make it clear why
this works. This algorithm's time complexity is $O(n)$, where $n$ is the sum
total of the number of vertices of all of the polygons being
tested~\autocite{geeksforgeekspolygon}.

@@

On September 26\textsuperscript{th} we returned to Kinkaku-ji with a nearly
complete version of the ARuko in order to conduct some final testing. We met up
with Atticus, the IQP group, and our intern Hikaru and installed the beta
version of ARuko on each of their phones. With little instruction about how the
app works we had each of them try going through Kinkaku-ji while listening to
the tour and using the app's features. Each member of our team also installed
the beta version so we could fuzz test it.

This was our first time trying the AR image recognition on the actual signs at
Kinkaku-ji, rather than photographs of the signs, and it worked quite well.
Vuforia was able to recognize all of the signs, even in different lighting than
when the reference images were taken. For image targets that were small, far
away, or obscured by shadows image recognition was slower, but Vuforia was
always able to recognize them eventually. We discovered that the targets that
worked best were large, had a lot of high-contrast text, and were uniformly lit.

While testing we discovered some issues with the design of the tour. One region
was completely misplaced, so the audio played at the wrong time while walking
through the area. Several other regions were too big, so the audio started
playing long before the user was actually near the feature it was discussing.
Finally, one of the image targets had the wrong text in its information pop-up.
These were all easy bugs to fix, but if we might not have noticed them if we
had not tested the app on site.

Another major bug we discovered was that the GPS stopped updating when not on
the main screen. This means that if you were in AR camera mode the app would not
trigger new audio when you walked into a new region. This was caused by the GPS
script being attached to a UI element on the main screen, so it was resolved
simply by moving this script.

After having Atticus go through the tour on his phone he also discovered several
bugs and tweaks he wanted to make to the UI. The clickable information button on
image targets was made larger so it is easier to see. The UI buttons in the
bottom menu bar were also made larger and easier to press. The text ``Main'' was
added under the central button that brings you to the screen with the images and
transcript, so it was more clear what that button does. The header text at the
top was too big, and sometimes overflowed onto other UI elements.

Testing with Atticus revealed another user interface issue we had not
considered.  Many modern smartphones, such as Atticus's Samsung Galaxy S10+,
have holes or notches cut out of the screen for cameras, speakers, and other
hardware (see Figures \ref{fig:galaxyS10Plus} and \ref{fig:iPhoneX}). We had
been designing our UI for rectangular phone screens, so the Galaxy S10+'s ``hole
punch'' covered some UI elements in the top right corner. To account for this
issue we added more padding to the top of the UI.

After going through Kinkaku-ji with the app twice we had each test participant
fill out a simple survey giving their thoughts on the app. The full results of
these surveys can be found in Appendix~\ref{sec:testingSurveyResults}.

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{galaxy-s10+.jpg}
	\caption[A Samsung Galaxy S10+ phone with distinctive ``hole punch''
	cameras]{A Samsung Galaxy S10+ phone with distinctive ``hole punch''
		cameras~\autocite{yoo2019}}
	\label{fig:galaxyS10Plus}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{iphone-x.jpg}
	\caption[An iPhone X with a large notch]{An iPhone X with a large
		notch~\autocite{yoo2017}}
	\label{fig:iPhoneX}
\end{figure}

@@

\subsection{3D Spatialized Audio Tour}
\label{sec:3dSpatializedAudioTour}

@@

\section{Testing Survey Results}
\label{sec:testingSurveyResults}

After testing a near-complete prototype of ARuko at Kinkaku-ji on September
26\textsuperscript{th}, we had each test subject fill out a simple survey with
their thoughts on the app. The full results are listed below.

% for tabularx
% \newcolumntype{L}{>{\raggedright\arraybackslash\footnotesize}X}%

\begin{table}[h]
\begin{singlespace}
\begin{tabulary}{\textwidth}{ L | L | L | L | L | L }
	I enjoyed the audio tour & The image gallery added to the audio tour & I
	found the AR translation feature helpful & I found the AR map overlay
	helpful & The AR features were easy to use & Do you have any other thoughts
	on how to improve the experience? \\
	\hline

	Strongly agree & Agree & Strongly agree & Strongly agree & Agree & I thought
	the idea about a sound playing before the audio starts is a really good
	idea! \\

	Agree & Agree & Agree & Neutral & Neutral & Add a audio queue when a new
	track starts. Make the AR buttons bigger/easier to click. \\

	Agree & Agree & Strongly agree & Neutral & Agree & Increasing GPS accuracy
	of course. Adding a tracking "you are here" marker to the route. \\

	Strongly agree & Strongly agree & Strongly agree & Strongly agree & Strongly
	agree & Typo in the text on 4/11 towards the end \\

	Agree & Agree & Strongly agree & Disagree & Neutral & Zoom in ar mode \\
\end{tabulary}
\end{singlespace}
\caption{Results of final field test survey}
\label{tab:testingSurveyResults}
\end{table}
